R Notebook

### 2022-05-07 draft_nb.Rmd
5/6 update 3, the model is ready!!!!!!!

# Modeling with Real Data
```{r}
# Load data
gdp_file = "https://github.com/SamL153/bayesian_stats_project/raw/master/gdp.csv"
inflation_file = "https://github.com/SamL153/bayesian_stats_project/raw/master/inflation_rate.csv"
interest_file = "https://github.com/SamL153/bayesian_stats_project/raw/master/interest_rate.csv"
msupply_file = "https://github.com/SamL153/bayesian_stats_project/raw/master/money_supply.csv"
mvelocity_file = "https://github.com/SamL153/bayesian_stats_project/raw/master/money_velocity.csv"
Q = read_csv(gdp_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1980-01-01'))
P = read_csv(inflation_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1980-01-01')) %>%
  mutate(CPIAUCSL_PC1 = as.double(CPIAUCSL_PC1)/100)
I = read_csv(interest_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1980-01-01')) %>%
  mutate(DFF = as.double(DFF)/100)
M = read_csv(msupply_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1980-01-01'))
V = read_csv(mvelocity_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1980-01-01'))
monthly_train <- P %>% inner_join(I, by = 'DATE') %>% inner_join(M, by = 'DATE') %>% left_join(Q, by = 'DATE') %>% left_join(V, by = 'DATE') %>%
  rename(P = CPIAUCSL_PC1, I = DFF, M = M2REAL, Q = GDPC1, V = M2V) %>%
  filter(DATE < as.POSIXlt('2021-07-01')) %>%
  mutate(time = 1:n(),
         Q = na.locf(Q),
         V = na.locf(V),
         m = month(DATE))
monthly_test <- P %>% inner_join(I, by = 'DATE') %>% inner_join(M, by = 'DATE') %>% left_join(Q, by = 'DATE') %>% left_join(V, by = 'DATE') %>%
  rename(P = CPIAUCSL_PC1, I = DFF, M = M2REAL, Q = GDPC1, V = M2V) %>%
  filter(DATE >= as.POSIXlt('2021-07-01')) %>%
  mutate(time = 1:n(),
         Q = na.locf(Q),
         V = na.locf(V),
         m = month(DATE))
I_m1_train <- rbind(I[1,], I) %>%
  filter(DATE < as.POSIXlt('2021-06-01')) %>%
  rename(I_m1 = DFF)
I_m1_test <- I %>%
  filter(DATE >= as.POSIXlt('2021-06-01'), DATE < as.POSIXlt('2022-02-01')) %>%
  rename(I_m1 = DFF)
P_m1_train <- read_csv(inflation_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1979-12-01'), DATE < as.POSIXlt('2021-06-01')) %>%
  mutate(CPIAUCSL_PC1 = as.double(CPIAUCSL_PC1)/100) %>%
  rename(P_m1 = CPIAUCSL_PC1)
P_m1_test <- (read_csv(inflation_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('2021-06-01'), DATE < as.POSIXlt('2022-02-01')) %>%
  mutate(CPIAUCSL_PC1 = as.double(CPIAUCSL_PC1)/100) %>%
  rename(P_m1 = CPIAUCSL_PC1))
monthly_train <- cbind(monthly_train, P_m1_train[,2], I_m1_train[,2])
monthly_test <- cbind(monthly_test, P_m1_test[,2], I_m1_test[,2])
```

@@

```{r}
plot(model, 'components')
pred1 <- predict(model, horizon = 8, newdata = monthly_test)
plot(pred1)
```

```{r}
forecast_months = 8 # number of months forward to forecast
set.seed(123456)
y_max = .1
y_axis = list(
  coord_cartesian(ylim = c(-0.02, y_max), expand = FALSE),
  scale_y_continuous(labels = scales::percent),
  theme(axis.text.y = element_text(vjust = 0.05))
)
title = labs(x = NULL, y = NULL, subtitle = "US inflation over time")
```

>>>>

# Modeling with Real Data
```{r}
# Load data
gdp_file = "https://github.com/SamL153/bayesian_stats_project/raw/master/gdp.csv"
inflation_file = "https://github.com/SamL153/bayesian_stats_project/raw/master/inflation_rate.csv"
interest_file = "https://github.com/SamL153/bayesian_stats_project/raw/master/interest_rate.csv"
msupply_file = "https://github.com/SamL153/bayesian_stats_project/raw/master/money_supply.csv"
mvelocity_file = "https://github.com/SamL153/bayesian_stats_project/raw/master/money_velocity.csv"
Q = read_csv(gdp_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1980-01-01'))
P = read_csv(inflation_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1980-01-01')) %>%
  mutate(CPIAUCSL_PC1 = as.double(CPIAUCSL_PC1)/100)
I = read_csv(interest_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1980-01-01'), !is.na(DFF)) %>%
  mutate(DFF = as.double(DFF)/100)
M = read_csv(msupply_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1980-01-01'))
V = read_csv(mvelocity_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1980-01-01'))
monthly_train <- P %>% inner_join(I, by = 'DATE') %>% inner_join(M, by = 'DATE') %>% left_join(Q, by = 'DATE') %>% left_join(V, by = 'DATE') %>%
  rename(P = CPIAUCSL_PC1, I = DFF, M = M2REAL, Q = GDPC1, V = M2V) %>%
  filter(DATE < as.POSIXlt('2021-07-01')) %>%
  mutate(m = month(DATE),
         V = na.locf(V))
monthly_test <- P %>% inner_join(I, by = 'DATE') %>% inner_join(M, by = 'DATE') %>% left_join(Q, by = 'DATE') %>% left_join(V, by = 'DATE') %>%
  rename(P = CPIAUCSL_PC1, I = DFF, M = M2REAL, Q = GDPC1, V = M2V) %>%
  filter(DATE >= as.POSIXlt('2021-07-01')) %>%
  mutate(m = month(DATE),
         V = na.locf(V))
I_m1_train <- rbind(I[1,], I) %>%
  filter(DATE < as.POSIXlt('2021-06-01')) %>%
  rename(I_m1 = DFF)
I_m1_test <- I %>%
  filter(DATE >= as.POSIXlt('2021-06-01'), DATE < as.POSIXlt('2022-03-01')) %>%
  rename(I_m1 = DFF)
P_m1_train <- read_csv(inflation_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('1979-12-01'), DATE < as.POSIXlt('2021-06-01')) %>%
  mutate(CPIAUCSL_PC1 = as.double(CPIAUCSL_PC1)/100) %>%
  rename(P_m1 = CPIAUCSL_PC1)
P_m1_test <- (read_csv(inflation_file, show_col_types = F) %>%
  filter(DATE >= as.POSIXlt('2021-06-01'), DATE < as.POSIXlt('2022-03-01')) %>%
  mutate(CPIAUCSL_PC1 = as.double(CPIAUCSL_PC1)/100) %>%
  rename(P_m1 = CPIAUCSL_PC1))
monthly_train <- cbind(monthly_train, P_m1_train[,2], I_m1_train[,2]) %>%
  mutate(time = 1:n())
monthly_test <- cbind(monthly_test, P_m1_test[,2], I_m1_test[,2]) %>%
  mutate(time = 1:n())
```

@@

```{r}
plot(model, 'components')
pred1 <- predict(model, horizon = 9, newdata = monthly_test)
plot(pred1)
```

```{r}
forecast_months = 9 # number of months forward to forecast
set.seed(123456)
y_max = .1
y_axis = list(
  coord_cartesian(ylim = c(-0.02, y_max), expand = FALSE),
  scale_y_continuous(labels = scales::percent),
  theme(axis.text.y = element_text(vjust = 0.05))
)
title = labs(x = NULL, y = NULL, subtitle = "US inflation over time")
```
